Dynamics of Laterally Propagating Flames in X-ray Bursts. II. Realistic Burning \& Rotation

### 2020-11-19 xrb2/paper.tex
added some text describing the temperature phase plots

@@

>>>>

Looking at the phase plots in Figures~\ref{fig:urho_hot}-\ref{fig:abar_hot}, we see:
\begin{itemize}
    \item The $u$-$\rho$ plot in Figure~\ref{fig:urho_hot} shows that the horizontal velocity when $T_{\rm star} = 3\times10^8$~K is sufficiently greater than for the two cooler runs. This is consistent with the plot of the flame front position, where we saw that the hottest flame was significantly faster at later times than the cooler flames.
    \item The $u$-$v$ plot in Figure~\ref{fig:uv_hot} further demonstrates this, as again we see that the magnitude of the velocity of the flame for the hottest run is significantly larger. Also of interest in these plots is that the coolest run does not seem to have developed the characteristic vortex structure at the burning front (i.e. where $\dot{e}_{\rm nuc}$ is greatest) that can be clearly seen for the hotter runs.
    \item The $\overline{A}$-$T$ plot in Figure~\ref{fig:abar_hot} suggests that the actual reactions happening in the hottest run may be different than for the cooler runs. Not only is the flame itself significantly hotter overall, but there is a large causally connected region across a wide range of $\overline{A}$. This indicates that the hotter temperature has facilitated significant burning in reaction pathways that were not favored at the lower temperatures.
\end{itemize}

@@

%======================================================================
% Conclusions
%======================================================================
\section{Discussion and Conclusions}\label{Sec:conclusions}

tl;dr: faster rotation and/or hotter surface temperature = more burning.
